---
title: "Analysis"
author: "Keven Quach"
date: "4/13/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(arules)
library(arulesViz)
library(corrplot)
library(RColorBrewer)
options(scipen = 100)
```

## R Markdown

### Only clean data will be used (less entrants than filtered) as even further filtering will be applied.
```{r import data}
users <- read.csv("data/users_filtered.csv", encoding="UTF-8")
anime <- read.csv("data/anime_filtered.csv", encoding="UTF-8")
animelists <- read.csv("data/animelists_filtered.csv", encoding="UTF-8")
```


```{r}
users <- users %>% select(username, user_id, user_completed, gender, stats_mean_score)
anime <- anime %>% select(anime_id, title, type, episodes, status, rating, score, scored_by, rank, popularity, favorites, genre)
animelists <- animelists %>% select(username, anime_id, my_watched_episodes, my_score, my_status)
#save.image(file="clean.RData")
```

my_status in animelists tables contains integer values. This is their semantics:

1: watching
2: completed
3: on hold
4: dropped
6: plan to watch
--> only completed anime are relevant

# More filtering
```{r}

users <- users %>% filter(user_completed >= 10)
anime <- anime %>% filter(status == "Finished Airing")
animelists <- animelists %>% filter(my_status == 2)
```

```{r}
users$gender <- as.factor(users$gender)
anime$type <- as.factor(anime$type)
anime$status <- as.factor(anime$status)
anime$rating <- as.factor(anime$rating)

str(users)
str(anime)
str(animelists)
```
# Concerning the report, this should be a 2-4 pages summary where you describe the task, your approach to it, how you evaluate it, and the results. I expect at least a live demo at the end of your project - of course, creating a recommendation web app would be a nice bonus, but only if you have time.
# descriptive analytics/visualisation and frequent itemset mining

# Descriptive plots 
```{r}
anime_grouped_rating <- anime %>% 
  group_by(rating) %>% 
  summarise(scored_by = sum(scored_by), favorites = sum(favorites)) 
anime_grouped_rating <- anime_grouped_rating[c(1,4,3,5,6,7),]
anime_grouped_rating$rating <- factor(anime_grouped_rating$rating, levels = anime_grouped_rating$rating)
anime_grouped_rating %>% 
  ggplot(aes(rating, scored_by)) +
  geom_bar(stat = "identity") +
  ggtitle("Number of anime scored - grouped by age ratings") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) 

# anime_grouped_rating %>% 
#   ggplot(aes(rating, favorites)) +
#   geom_bar(stat = "identity") +
#   ggtitle("Number of anime favorited - grouped by age ratings") +
#   theme(axis.text.x = element_text(angle = 45, hjust = 1)) 

cor <- anime %>% select(episodes, score, scored_by, rank, popularity, favorites) %>% cor(use ="complete.obs")
col <- colorRampPalette(c("#BB4444", "#EE9988", "#FFFFFF", "#77AADD", "#4477AA"))
corrplot(cor, method="color", col=col(200),  
     diag=FALSE, # tl.pos="d", 
         type="upper", order="hclust", 
     title="Correlation matrix of anime variables", 
         addCoef.col = "black", # Add coefficient of correlation
         # Combine with significance
         # hide correlation coefficient on the principal diagonal
     mar=c(0,0,1,0) # http://stackoverflow.com/a/14754408/54964
         )
```
# Transform to transaction format for arules
```{r}
transactions_df = merge(x = animelists[ , c("anime_id", "username")], y = anime[ , c("anime_id", "title")], by = "anime_id")
transactions_df$anime_id <- NULL
#ddply(dataframe, variables_to_be_used_to_split_data_frame, function_to_be_applied)
transaction_data <- plyr::ddply(transactions_df,"username",
                       function(df1)paste(df1$title,
                       collapse = "|"))
names(transaction_data)[names(transaction_data) == 'V1'] <- 'items'
# more than 10 anime need to be in a transaction
transaction_data <- transaction_data %>% filter(str_count(items, "\\|") >= 9)
rm(transactions_df)

write.csv(transaction_data$items,"data/transactions.csv", quote = FALSE, row.names = FALSE)

```

```{r}
tr <- read.transactions("data/transactions.csv", format = 'basket', sep="|")

summary(tr)
itemFrequencyPlot(tr,topN=20, type="relative",col=brewer.pal(8,'Pastel2'), cex.names=.75, main="Absolute Item Frequency Plot", ) 

```
```{r}
association.rules <- apriori(tr, parameter = list(supp=0.001, conf=0.9,maxlen=4))
summary(association.rules)
inspect(association.rules[1:10])
plot(association.rules)
```


```{r}
str(animelists)
rules <- apriori(animelists, parameter = list(supp = 0.5, conf = 0.9, target = "rules"))
summary(rules)
inspect(head(rules, by = "lift"))
```


