---
title: "Analysis"
author: "Keven Quach"
date: "4/13/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(arules)
library(arulesViz)
library(corrplot)
library(RColorBrewer)
library(stringr)
library(xtable)
options(scipen = 100)
```

## R Markdown

### Only clean data will be used (less entrants than filtered) as even further filtering will be applied.
```{r import data}
users <- read.csv("data/users_filtered.csv", encoding="UTF-8")
anime <- read.csv("data/anime_filtered.csv", encoding="UTF-8")
animelists <- read.csv("data/animelists_filtered.csv", encoding="UTF-8")
```


```{r}
users <- users %>% select(username, user_id, user_completed, gender, stats_mean_score)
anime <- anime %>% select(anime_id, title, type, episodes, status, rating, score, scored_by, rank, popularity, favorites, genre)
animelists <- animelists %>% select(username, anime_id, my_finish_date, my_last_updated, my_status)
#save.image(file="clean.RData")
```

my_status in animelists tables contains integer values. This is their semantics:

1: watching
2: completed
3: on hold
4: dropped
6: plan to watch
--> only completed anime are relevant

# More filtering
```{r}

users <- users %>% filter(user_completed >= 10)
anime <- anime %>% filter(status == "Finished Airing")
animelists <- animelists %>% filter(my_status == 2) %>% filter(my_last_updated != 0) %>% arrange(my_last_updated)

```

```{r}
users$gender <- as.factor(users$gender)
anime$type <- as.factor(anime$type)
anime$status <- as.factor(anime$status)
anime$rating <- as.factor(anime$rating)
anime$title <- HTMLdecode(anime$title)

str(users)
str(anime)
str(animelists)
```
# Concerning the report, this should be a 2-4 pages summary where you describe the task, your approach to it, how you evaluate it, and the results. I expect at least a live demo at the end of your project - of course, creating a recommendation web app would be a nice bonus, but only if you have time.
# descriptive analytics/visualisation and frequent itemset mining

# Descriptive plots 
```{r}
anime_grouped_rating <- anime %>% 
  group_by(rating) %>% 
  summarise(scored_by = sum(scored_by), favorites = sum(favorites)) 
anime_grouped_rating <- anime_grouped_rating[c(1,4,3,5,6,7),]
anime_grouped_rating$rating <- factor(anime_grouped_rating$rating, levels = anime_grouped_rating$rating)
anime_grouped_rating %>% 
  ggplot(aes(rating, scored_by)) +
  geom_bar(stat = "identity") +
  theme_minimal(base_size = 14) +
  theme(axis.text.x = element_text(angle = 15, hjust = 1, size=14)) +
  xlab("Rating") + ylab("Number of people scored")+
  ggsave("plots/scored_by_rating.png")

cor <- anime %>% select(episodes, score, scored_by, rank, popularity, favorites) %>% cor(use ="complete.obs")
col <- colorRampPalette(c("#BB4444", "#EE9988", "#FFFFFF", "#77AADD", "#4477AA"))
corrplot(cor, method="color", col=col(200),  
     diag=FALSE, # tl.pos="d", 
         type="upper", order="hclust", 
     #title="Correlation matrix of anime variables", 
         addCoef.col = "black", # Add coefficient of correlation
         # Combine with significance
         # hide correlation coefficient on the principal diagonal
     mar=c(0,0,1,0) # http://stackoverflow.com/a/14754408/54964
         )


# Change density plot line colors by groups
ggplot(users, aes(x=stats_mean_score, color=gender)) +
  scale_x_continuous(breaks = scales::pretty_breaks(n = 10)) +
  geom_density() +
  theme_minimal(base_size = 14) +
  xlab("Average score") + ylab("Density")+
  theme(legend.position=c(0.1, 0.8)) +
  ggsave("plots/density_mean_score.png")

ggplot(users, aes(x=user_completed, color=gender)) + 
  scale_x_continuous(breaks = scales::pretty_breaks(n = 5)) +
  stat_ecdf(geom = "step") +
  theme_minimal(base_size = 14) +
  xlab("Number of completed anime") + ylab("Percent")+
  theme(legend.position=c(0.9, 0.2), plot.margin = unit(c(0,.5,0,0), "cm")) +
  ggsave("plots/cdf_completed_anime.png")
sum(users$user_completed >= 1000)
```
# Transform to transaction format for arules
```{r}
transactions_df <- merge(x = animelists[ , c("anime_id", "username", "my_last_updated")], y = anime[ , c("anime_id", "title")], by = "anime_id")
transactions_df <- transactions_df %>% arrange(my_last_updated) 
transactions_df$anime_id <- NULL
transactions_df$my_last_updated <- NULL

transaction_data <- plyr::ddply(transactions_df,"username",
                       function(df1)paste(df1$title,
                       collapse = "|"))
names(transaction_data)[names(transaction_data) == 'V1'] <- 'items'
# more than 10 anime need to be in a transaction
transaction_data <- transaction_data %>% filter(str_count(items, "\\|") >= 9)
rm(transactions_df)

write.csv(transaction_data$items,"data/transactions.csv", quote = FALSE, row.names = FALSE)

```

```{r}
tr <- read.transactions("data/transactions.csv", format = 'basket', sep="|", quote = "")

summary(tr)
itemFrequencyPlot(tr,topN=20, type="relative",col=brewer.pal(8,'Pastel2'), cex.names=.75)

```

```{r}
fillwords <- c("no", "to", "of", "wa", "the")
symbols <- "\\{|\\}|\\.|\\!|\\:|\\,|\\/|\\/|'"
flag_same_series <- function(df) {
  # clean titles for common symbols and fillwords
  lhs <- str_trim(str_replace_all(tolower(df["lhs"]), symbols, " "))
  rhs <- str_trim(str_replace_all(tolower(df["rhs"]), symbols, " "))
  lhs_array <- str_split(lhs, " ")[[1]]
  rhs_array <- str_split(rhs, " ")[[1]]
  lhs_array = lhs_array[!(lhs_array %in% fillwords)]
  rhs_array = rhs_array[!(rhs_array %in% fillwords)]
  any(lhs_array %in% rhs_array)
}

get_rules_df <- function (rules) {
  data.frame(
  lhs = labels(lhs(rules)),
  rhs = labels(rhs(rules)), 
  rules@quality)
} 
get_recommendations <- function(title, tr, supp, conf) {
  rules_rhs <- apriori(tr, parameter = list(supp=supp, conf=conf, minlen=2, maxlen = 2),appearance = list(default="lhs",rhs=title))
  rules_lhs <- apriori(tr, parameter = list(supp=supp, conf=conf, minlen=2, maxlen = 2),appearance = list(default="rhs",lhs=title))
  rules <- c(rules_rhs, rules_lhs)
  rules_df <- get_rules_df(rules)
  flags_series <- apply(X = select(rules_df, c("lhs", "rhs")), MARGIN = 1, flag_same_series)
  filtered.rules <- rules[-which(flags_series == TRUE, arr.ind=TRUE)]
  print(table(flags_series))
  filtered.rules
}
```


```{r}
association.rules <- apriori(tr, parameter = list(supp=0.1, conf=0.8, minlen=2, maxlen=2))
summary(association.rules)
inspect(association.rules[1:10])

rules_df <- get_rules_df(association.rules)
flags_series <- apply(X = select(rules_df, c("lhs", "rhs")), MARGIN = 1, flag_same_series)
filtered.rules <- association.rules[-which(flags_series == TRUE, arr.ind=TRUE)]

summary(filtered.rules)

png(filename="plots/rules_unfiltered.png") +
plot(association.rules) +
dev.off()

png(filename="plots/rules_filtered.png") +
plot(filtered.rules) +
dev.off()
plot(head(filtered.rules, n = 100, by = "confidence"), method = "graph", engine = "htmlwidget")

plot(association.rules) +
plot(filtered.rules) 
xtable(head(get_rules_df(filtered.rules) %>% arrange(desc(lift)) %>% select(lhs, rhs, lift), 10))


```



```{r}
title <- "Prison School"
single_rules <- get_recommendations(title, tr, 0.01, 0.7)
inspect(single_rules)
plot(single_rules, engine="plotly")
xtable(get_rules_df(single_rules) %>% arrange(desc(lift)) %>% select(lhs, rhs, lift))
```



```{r}
```


